### 2012-06-29 inst/examples/bias_table.Rmd
bias table updated

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
scenarios <- names(par_list) 
print(xtable(matrix(means$V1, nrow=length(scenarios), dimnames=list(scenarios, scenarios))), type="html")
print(xtable(matrix(sds$V1, nrow=length(scenarios), dimnames=list(scenarios, scenarios))), type="html")
````

>>>>

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
scenarios <- c("low", "med", "high")
print(xtable(matrix(means$V1, nrow=length(scenarios), dimnames=list(scenarios, scenarios))), type="html")
print(xtable(matrix(sds$V1, nrow=length(scenarios), dimnames=list(scenarios, scenarios))), type="html")
````
